Statically Typed Web Programming using Scala

### 2012-12-19 papers/ecoop2013/repairing.tex
morning commit

\begin{table}
\centering
\begin{tabular}{| l | c | c | c | c | c | c | c | c |}
\hline
& jQuery & TypeScript & Roy & GWT & Kotlin & Opa & Dart & js-scala \\
\hline
Type safe event handling & & & & *** & & & & *** \\
\hline
DOM definition & * & & & *** & ** & *** & * & *** \\
\hline
Asynchronous programming & ** & & *** & & & *** & ** & *** \\
\hline
Null references & ** & & *** & & * & ** & & *** \\
\hline
Type coercion & & & & * & * & * & * & *** \\
\hline
%General programming language features & * & ** & ** & * & *** & ? & * & *** \\
%\hline
Static typing & & * & ** & ** & ** & ** & * & ** \\
\hline
Easiness for defining libraries & ** & *** & *** & *** & *** & *** & *** & * \\
\hline
Client-server code sharing & & * & * & * & * & *  & * & *** \\
\hline
\end{tabular}
\caption{Support level of Web programming features by mainstream tools. Zero star means that the feature is not supported
at all, three stars mean a strong support.}
\label{comparison}
\end{table}

Several model-driven methodologies for creating web applications have been proposed, including
\cite{schwabe1996systematic,lima2003modeling,ceri2000web,koch2001authoring,pastor2003oows,valverde2007mda,vdovjak2003engineering,kraus2007model,nunes2006rapid,brambilla2008designing,valderas2007transformational,van2006hera,Groenewegen08_WebDSL}.
Many of them follow the standard top-down MDE vision in providing abstractions and code generators, nevertheless
these cannot be easily customized or generate only application skeletons.

>>>>

\begin{table}
\centering
\begin{tabular}{| l | c | c | c | c | c | c | c | c |}
\hline
& jQuery & TypeScript & Roy & GWT & Kotlin & Opa & Dart & js-scala \\
\hline
Type safe event handling & & & & *** & & & & *** \\
\hline
DOM definition & * & & & *** & ** & *** & * & *** \\
\hline
Asynchronous programming & ** & & *** & & & *** & ** & *** \\
\hline
Null references & ** & & *** & & * & ** & & *** \\
\hline
Type coercion & & & & * & * & * & * & *** \\
\hline
%General programming language features & * & ** & ** & * & *** & ? & * & *** \\
%\hline
Static typing & & * & ** & ** & ** & ** & * & ** \\
\hline
Easiness for defining libraries & ** & *** & *** & *** & *** & *** & *** & * \\
\hline
Client-server code sharing & & * & * & * & * & *  & * & *** \\
\hline
\end{tabular}
\caption{Support of Web programming features by mainstream tools. Zero star means that the feature is not supported
at all, three stars mean a strong support.}
\label{comparison}
\end{table}

Several model-driven methodologies for creating web applications have been proposed, including
\cite{schwabe1996systematic,lima2003modeling,ceri2000web,koch2001authoring,pastor2003oows,valverde2007mda,vdovjak2003engineering,kraus2007model,nunes2006rapid,brambilla2008designing,valderas2007transformational,van2006hera,Groenewegen08_WebDSL}.
Many of them follow the standard top-down MDE vision in providing abstractions and code generators, nevertheless
these cannot be easily customized or they generate only application skeletons.
